\documentclass{mycv}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome}
\thispagestyle{empty} 

\name{Daniel Ko} 
\email{danielhbko@gmail.com}
\homepage{https://ko28.github.io}
\github{ko28}
\linkedin{daniel-ko1}

\begin{document}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\subsection{University of Wisconsin - Madison}[Madison, WI]
\begin{itemize}[label={}]
  \item B.S.\ in Computer Science \printdate{Expected May 2023}
  \item 3.9/4.0 Cumulative GPA
  %\item {Relevant Coursework: Discrete Mathematics, Linear Algebra, Multivariable Calculus, Object oriented programming, Data Structures, Algorithms, Artificial Intelligence, Computer Vision, Operating Systems}
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Professional \\ Experience}

\subsection{Zendesk}[Madison, WI]
\begin{positions}
  \entry{Software Engineering Intern}{Oct 2020~--~June 2021}
\end{positions}
\begin{itemize}
\iffalse
  \item {
     Collaborated closely with local and global team members to build large scale, efficient, and safe \textbf{CI/CD} pipelines that deploy to over dozens of servers globally for 300 million end users.
  }
\fi
  \item {
  Created tool to provision a \textbf{Spinnaker} development environment via \textbf{Terraform} on \textbf{AWS}, containing a fully-fledged Kubernetes cluster for test deployment. Reduced developer setup time from a full day to 10 minutes. 
  }
  \item {
  Extended the collection of \textbf{Spinnaker} metrics by adding support for stage rollback events. Collected and visualized metrics using \textbf{Datadog} and created alerts for abnormal stage event behaviors. 
  }
  \item {
  Created a secret manager container for \textbf{Hashicorp Vault} from the ground up using the sidecar pattern. Fully written in \textbf{Go}, it supports Auto-Auth via a \textbf{Kubernetes} service account token, fetching and auto refreshing Vault KV secrets, and generating \textbf{AWS STS} tokens.
  }
 \end{itemize}
  
\subsection{TDS Telecom}[Madison, WI]
\begin{positions}
  \entry{Software Engineering Intern}{Sept 2019~--~Oct 2020}
\end{positions}
\begin{itemize}
  \item {
  Addressed regular production bugs and improvements in enterprise \textbf{Java}
applications using \textbf{JIRA} to prioritize tasks and utilized \textbf{CI/CD} pipelines for
rapid development and deployment.
  }
  \item {
  Developed \textbf{Python} script that used the \textbf{ArcGIS API} to automate uploading
service definition files to and from a remote server, increased upload speeds
by 80\%.
}
  \item {
  Developed, refactored, and upgraded legacy \textbf{Perl} web applications and scripts
on an Operations Support Systems (NetExpert) server, which interacted with
internal \textbf{RESTful} services and \textbf{SQL} servers. Web applications used by more than 1,000
field technicians.
  }
\end{itemize}


\subsection{Juni Learning}[Remote]
\begin{positions}
  \entry{Computer Science Instructor}{Sept 2019~--~Jan 2020}
\end{positions}
\begin{itemize}
  \item {
  Individually taught 8 students aged 8-16 \textbf{Scratch}, \textbf{Python}, and \textbf{Java} (AP Computer Science). 
  }
  \item{
    Selected to be one of the few trial instructors to represent Juni Learning to prospective students.
  Successfully taught trial sessions resulting in more than 50\% enrollment rate.
  }
  \item{
    Taught with a pedagogical philosophy based on project-based learning and praxis.
    Emphasized critical thinking and risk-taking during lessons by presenting myself as a
    knowledgeable collaborator rather than an source of infallible facts. 
  }
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}

%
\subsection{Automatic Chord Recognition by Music Source Separation
 \href{https://ko28.github.io/chord-transcription/}{\faicon{github}
}
}
\begin{itemize}
  \item {
    Researched a novel automatic chord recognition method where songs are preprocessed by a music source separation model before being fed into a convolutional recurrent neural network. 
  }
\iffalse
\item{
Experiments have showed that the model trained with song computed from music source separation performed similar on average compared to a model trained on the original dataset.
}
\fi 
 \end{itemize}


\subsection{Google Summer of Code 2021 Participant for Spinnaker\
    \href{https://github.com/spinnaker/try.spinnaker.io}{\faicon{github}}
}
\begin{itemize}
  \item {
    Developed a hosted playground version of Spinnaker aimed for new users to test out its UI and core features.
  }
 \item{
 Infrastructure as code via \textbf{Terraform} to provision environment on \textbf{AWS} using an EKS cluster. Deployment of Spinnaker via Armory's OOS Spinnaker Operator.
 }
 \item{
 AWS Load Balancer Controller to expose deployments, private ECR registry and image security policies via Portieris. 
}
\item{
    Implemented AuthN via Google OAuth 2.0 and AuthZ rules via a custom Spinnaker plugin.
}
 \end{itemize}
%%%%%%%%%%%%%%%%%%%
\section{Skills}
\begin{description}
  \item[Programming] Java, Python, Perl, C, MATLAB, SQL, Bash, Go, HTML, CSS, Javascript
  \item[Tools] Docker, Kubernetes, Terraform, AWS, Spinnaker, Git, JIRA, Jenkins, *nix, \LaTeX 
  \item[Languages] English, Korean
  % \item[Miscellaneous] Red Cross Adult and Pediatric First Aid/CPR/AED Certification
\end{description}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\section{Awards}
\begin{itemize}
    \item{Language Flagship Scholarship, U.S. National Security
    Education Program \printdate{2021}}
    \item{Foreign Language and Area Studies (FLAS) Fellowship, U.S. Department of Education \printdate{2020}}
    \item {STEM Engagement, Altitude, Social Media Award, NASA Student Launch Initiative \printdate{2019}}
    \item {1st Place, Rocket for Schools Competition (cooperation with Gilroy and Ane Lab) \printdate{2018, 2019}}
    \item National Finalist, Team America Rocketry Challenge \printdate{2018}
\end{itemize}
\fi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty} 

\end{document}
